---
author: "Ben Chu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

# change echo = TRUE, when you want to start publishing to wordpress

library(RWordPress)
library(knitr)

options(WordpressLogin = c('chubenn' = 'FarsightedFlamingo1'),
        WordpressURL = 'https://chubenn.blog/xmlrpc.php')

knit2wp("IntroWordpressTemplate.Rmd", 
        title = "Intro to creating a Wordpress Template", 
        action = c("newPost"), 
        publish = FALSE)
```
### Brief Introduction to creating a basic Wordpress Template - Rmarkdown to Wordpress. 
Recently, I purchased a Wordpress account (4$/month - BIG BALLA) and have been posting both writing and coding through it. It was kinda tedious going through the whole copy and pasting motions for the [publication code](https://chubenn.blog/2018/11/28/look-at-me-now-im-the-one-posting-from-rmarkdown/), so I decided to write my own code to built a basic template and just reuse it. 

* Previous Better Posts/Stacks on the subject.
     + [Chester Ismay](http://ismayc.github.io/ecots2k16/template_pkg/)
     + [Sam Firke](https://stackoverflow.com/questions/40403569/rmarkdown-template-in-r-package-fails-when-i-add-create-dir-true)
     + [Joe and Marius](https://stackoverflow.com/questions/48675911/new-template-from-my-custom-package-is-not-appearing-in-rstudio)
     
#### Packages to use and folders
Start by making sure you have `devtools`, and making sure your working directory is in the right place.

`install.packages("devtools")`
Working directory is essentially the folder that R saves and operates out of. I usually have mine set to the Github Folders and push my repositories nightly. The `~/` fills in the information for the pathing so you don't have to set the entire `C:/Users/Ben/Documents/Github/Wordpress`.
`setwd("~/GitHub/Wordpress")`

#### Creating your template/package and skeleton directory
We are going to create a new package folder using the `create()` from devtools. I reccommend writing into a script because you will be starting over and over.

The name that you will be giving this folder is what you will be installing later. So don't name it anything stupid.
`devtools::create("WordpressTemplate")`

A fairly special path is going to be used from `dir.create` to specify the nested directories. I wouldn't reccommend deviating from the names but you can in one spot - `report`.

`dir.create("WordpressTemplate/inst/rmarkdown/remplates/report/skeleton", recursive = TRUE)`.
The `recursive = TRUE` arguement specifies if each individual folder should be created until the last folder. That is to say, everything inbetween `WordpressTemplate` and `Skeleton`

#### Creating the template.
At this point, open a new markdown like normal. *File -> New File -> Rmarkdown -> Document*. Add and delete as you will, I kept mine fairly simple. I want to mention that a line of code will keep the document updated on the time *r format(Sys.time(), '%d %B, %Y')*



`author: "Ben Chu"`

`date: "`r format(Sys.time(), '%d %B, %Y')`"`

`output: html_document`

```{r eval = FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(RWordPress)
library(knitr)

options(WordpressLogin = c('chubenn' = 'Password123(This isn't my password)'),
        WordpressURL = 'https://chubenn.blog/xmlrpc.php')

knit2wp("IntroWordpressTemplate.Rmd", 
        title = "Intro to creating a Wordpress Template", 
        action = c("newPost"), 
        publish = FALSE)
```

Save `IntrowordpressTemplate.Rmd` in the `skeleton` folder.

#### Creating template.yaml
A `.yaml` file is basically a data serialization lanauge for configuration. For these purposes, it provides information to the title/details/directory creation.
Let's make a new one *File -> New File -> -> Text File. 


name: Wordpress Template

description: Wordpress Template

create_dir:TRUE

Make sure to add a line break after the new line. Because it is a text file, it won't be properly read. `create_dir` = TRUE is a comment to create a new directory folder each time the template is used. Fairly useful if you have subfolders.

Then you will want to save the file in the `report` folder. *NOT THE SKELETON FOLDER* where it is defaulted. 

#### Installation and testing
This is where the script will come in handy for testing and retesting.

`devtools::install("WordpressTemplate")` to install the package, make sure to load it.
`library(WordpressTemplate)`

Followed by a clickthrough  *File -> New File -> Rmarkdown -> FROM TEMPLATE*.Where the new file should be located. I want to mention that it is a pretty good idea to add descriptions to the `.yaml` file. 

Good luck.

